### 2015-05-13 whoop.tex
updates

The simple concurrent programming model of \S\ref{sec:symbolicpairwise} is deliberately idealistic to make it easy to describe our symbolic verification technique. In practice, Linux drivers are written in C, we do not know up-front which are the entry points for a driver, drivers do not work with a cleanly specified set of named locks, and rather than having a given set of named shared variables, we have arbitrary memory accesses via pointers. We now explain how we have taken the conceptual ideas from \S\ref{sec:symbolicpairwise} and used them to build \whoop, a practical, fully automatic tool for detecting data races in drivers.

@@

\medskip\noindent\textbf{Practical Assumptions Related to Soundness}
%
\whoop is ``soundy''\footnote{http://soundiness.org/}~\cite{soundiness}: it aims in principle to perform a sound analysis that can prove absence of races, but suffers from some known sources of unsoundness, which we now comment on.

>>>>

The simple concurrent programming model of \S\ref{sec:symbolicpairwise} is deliberately idealistic to make it easy to describe our symbolic verification technique. In practice, Linux drivers are written in C, we do not know up-front which are the entry points for a driver, drivers do not work with a cleanly specified set of named locks, and rather than having a given set of named shared variables, we have arbitrary memory accesses via pointers. We now explain how we have taken the conceptual ideas from \S\ref{sec:symbolicpairwise} and used them to build \whoop\footnote{\url{https://github.com/pdeligia/whoop}}, a practical, fully automatic tool for detecting data races in drivers.

@@

\medskip\noindent\textbf{Practical Assumptions Related to Soundness}
%
\whoop is ``soundy''\footnote{\url{http://soundiness.org/}}~\cite{soundiness}: it aims in principle to perform a sound analysis that can prove absence of races, but suffers from some known sources of unsoundness, which we now comment on.
